---
title: "p8105_hw6_zg2486"
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)
library(SemiPar)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

# Problem 1


# Problem 2

#### Import and clean dataset.
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  filter(victim_age != "Unknown", victim_race != "Unknown", victim_sex != "Unknown" ) %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"),
    victim_age = as.numeric(victim_age)
  ) %>%
  filter(!city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>% 
  filter(victim_race %in% c("White", "Black")) 

```

#### GLM for Baltimore,MD.
```{r}
baltimore_model = 
  homicide_df %>% 
  filter(city_state == "Baltimore,MD") %>% 
  mutate(resolved = as.numeric(resolution == "solved")) %>%
  nest(data = -city_state) %>% 
  mutate(
    model = map(data, \(x) glm(resolved ~ victim_age + victim_race + victim_sex, 
                data = x, family = binomial())),
    results = map(model, broom::tidy, conf.int = TRUE)
  ) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    lower_ci = exp(conf.low), 
    upper_ci = exp(conf.high)
  ) %>% 
  select(city_state, OR, lower_ci, upper_ci) 

baltimore_model %>% 
  knitr::kable(digits = 3)
```
The adjusted odds ratio and 95 CI for solving homicides comparing male victims to female victims keeping all other variables fixed is 0.426 (95% CI: 0.324, 0.558).

#### Glm for each city.
```{r}
each_city_model = 
  homicide_df %>% 
  mutate(resolved = as.numeric(resolution == "solved")) %>%
  nest(data = -city_state) %>% 
  mutate(
    model = map(data, \(x) glm(resolved ~ victim_age + victim_race + victim_sex, 
                data = x, family = binomial())),
    results = map(model, broom::tidy, conf.int = TRUE)
  ) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    lower_ci = exp(conf.low),
    upper_ci = exp(conf.high)
  ) %>% 
  select(city_state, OR, lower_ci, upper_ci) 

each_city_model %>% 
  knitr::kable(digits = 3)
```

#### Create a plot that shows the estimated ORs and CIs for each city.
```{r}
each_city_plot =
  each_city_model %>% 
  arrange(OR) %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Estimated ORs and CIs by City",
    x = "city_state",
    y = "Estimated OR with CI"
  )

each_city_plot 
```
New York,NY and Albuquerque, NM has the lowest and highest adjusted OR for solving homicides comparing male victims to female victims keeping all other variables fixed, respectively. We can also see lots of cities have 95% CI across 1, which means there is no statistical significance of solving homicides comparing male victims to female victims for these cities.


# Problem 3
#### Import and clean data.
```{r}
bwt_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = 
        case_match(babysex,
            1 ~ "male",
            2 ~ "female"
        ),
    babysex = fct_infreq(babysex),
    frace = 
        case_match(frace,
            1 ~ "white",
            2 ~ "black", 
            3 ~ "asian", 
            4 ~ "puerto rican", 
            8 ~ "other"),
    frace = fct_infreq(frace),
    mrace = 
        case_match(mrace,
            1 ~ "white",
            2 ~ "black", 
            3 ~ "asian", 
            4 ~ "puerto rican",
            8 ~ "other"),
    mrace = fct_infreq(mrace),
    malform = as.logical(malform)) %>% 
  drop_na()
```

#### Propose a regression model for birthweight.
```{r}
bwt_model = 
  lm(bwt ~ babysex + bhead + blength + delwt + frace + gaweeks + momage + mrace + ppbmi
            + smoken + wtgain , data = bwt_df) 
  
birth_data = 
  bwt_df %>% 
  add_predictions(bwt_model) %>% 
  add_residuals(bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  geom_smooth() +
  labs(
    title = "Residuals vs. Fitted Values",
    x = "Fitted (Predicted) Values",
    y = "Residuals"
  )

birth_data
```

