---
title: "p8105_hw6_zg2486"
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)
library(SemiPar)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

# Problem 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

boot_sample =
  modelr::bootstrap(weather_df, 5000)

boot_sample_results =
  boot_sample %>%
  mutate(
    model = map(strap, ~ lm(tmax ~ tmin, data = as_tibble(.x))),
    r_squared = map_dbl(model, ~ broom::glance(.x)[["r.squared"]]),
    log_coef_product = map_dbl(model, ~ {
      coef_vals <- broom::tidy(.x) %>% 
      
      pull(estimate)
      
      log(coef_vals[1] * coef_vals[2])
    })
  )

r_squared_plot =
  boot_sample_results %>% 
  ggplot(aes(x = r_squared)) +
  geom_density(fill = "red", alpha = 0.5) +
  labs(title = "Distribution of R-squared of 5000 Bootstrap Samples",
       x = "R-squared",
       y = "Density"
       ) 

r_squared_plot

log_coef_product_plot = 
boot_sample_results %>%
  ggplot(aes(x = log_coef_product)) +
  geom_density(fill = "yellow", alpha = 0.5) +
  labs(title = "Distribution of log(beta0 ∗ beta1) of 5000 Bootstrap Samples",
       x = "log(beta0 * beta1)",
       y = "Density"
       )

log_coef_product_plot
```

```{r}

```


# Problem 2

#### Import and clean dataset.
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  filter(victim_age != "Unknown", victim_race != "Unknown", victim_sex != "Unknown" ) %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"),
    victim_age = as.numeric(victim_age)
  ) %>%
  filter(!city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>% 
  filter(victim_race %in% c("White", "Black")) 

```

#### GLM for Baltimore,MD.
```{r}
baltimore_model = 
  homicide_df %>% 
  filter(city_state == "Baltimore,MD") %>% 
  mutate(resolved = as.numeric(resolution == "solved")) %>%
  nest(data = -city_state) %>% 
  mutate(
    model = map(data, \(x) glm(resolved ~ victim_age + victim_race + victim_sex, 
                data = x, family = binomial())),
    results = map(model, broom::tidy, conf.int = TRUE)
  ) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    lower_ci = exp(conf.low), 
    upper_ci = exp(conf.high)
  ) %>% 
  select(city_state, OR, lower_ci, upper_ci) 

baltimore_model %>% 
  knitr::kable(digits = 3)
```
The adjusted odds ratio and 95 CI for solving homicides comparing male victims to female victims keeping all other variables fixed is 0.426 (95% CI: 0.324, 0.558).

#### Glm for each city.
```{r}
each_city_model = 
  homicide_df %>% 
  mutate(resolved = as.numeric(resolution == "solved")) %>%
  nest(data = -city_state) %>% 
  mutate(
    model = map(data, \(x) glm(resolved ~ victim_age + victim_race + victim_sex, 
                data = x, family = binomial())),
    results = map(model, broom::tidy, conf.int = TRUE)
  ) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    OR = exp(estimate),
    lower_ci = exp(conf.low),
    upper_ci = exp(conf.high)
  ) %>% 
  select(city_state, OR, lower_ci, upper_ci) 

each_city_model %>% 
  knitr::kable(digits = 3)
```

#### Create a plot that shows the estimated ORs and CIs for each city.
```{r}
each_city_plot =
  each_city_model %>% 
  arrange(OR) %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Estimated ORs and CIs by City",
    x = "city_state",
    y = "Estimated OR with CI"
  )

each_city_plot 
```
New York,NY and Albuquerque, NM has the lowest and highest adjusted OR for solving homicides comparing male victims to female victims keeping all other variables fixed, respectively. We can also see lots of cities have 95% CI across 1, which means there is no statistical significance of solving homicides comparing male victims to female victims for these cities.


# Problem 3
#### Import and clean data.
```{r}
bwt_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = 
        case_match(babysex,
            1 ~ "male",
            2 ~ "female"
        ),
    babysex = fct_infreq(babysex),
    frace = 
        case_match(frace,
            1 ~ "white",
            2 ~ "black", 
            3 ~ "asian", 
            4 ~ "puerto rican", 
            8 ~ "other"),
    frace = fct_infreq(frace),
    mrace = 
        case_match(mrace,
            1 ~ "white",
            2 ~ "black", 
            3 ~ "asian", 
            4 ~ "puerto rican",
            8 ~ "other"),
    mrace = fct_infreq(mrace),
    malform = as.logical(malform)) %>% 
  drop_na()
```

#### Propose a regression model for birthweight.
```{r}
bwt_model = 
  lm(bwt ~ babysex + bhead + blength + delwt + frace + gaweeks + momage + mrace + ppbmi
            + smoken + wtgain , data = bwt_df) 
  
birth_data = 
  bwt_df %>% 
  add_predictions(bwt_model) %>% 
  add_residuals(bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(
    title = "Residuals vs. Fitted Values",
    x = "Fitted (Predicted) Values",
    y = "Residuals"
  )

birth_data
```
In the regression model, I assumed that baby's birth weight would associate with baby’s sex, baby’s head circumference at birth, baby’s length at birth, father’s race, gestational age in weeks, mother’s age at delivery, mother’s race, mother’s pre-pregnancy BMI, average number of cigarettes smoked per day during pregnancy, mother’s weight gain during pregnancy. These variables are not only related to babies' characteristics, but also related to parental characteristics. 

#### Compare models by using cross-validation.
```{r}
cv_df = 
  crossv_mc(bwt_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_results_df = 
  cv_df %>% 
  mutate(
    bwt_model = map(train, \(x) lm(bwt ~ babysex + bhead + blength + delwt + frace + gaweeks + momage + mrace + ppbmi + smoken + wtgain , data = x)),
    main_effect_model = map(train, \(x) lm(bwt ~ blength + gaweeks, data = x)),
    interaction_model = map(train, \(x) lm(bwt ~ bhead * blength * babysex, data = x))
  ) %>% 
  mutate(
    rmse_bwt = map2_dbl(bwt_model, test, rmse),
    rmse_main_effect = map2_dbl(main_effect_model, test, rmse),
    rmse_interaction = map2_dbl(interaction_model, test, rmse)
  )

cv_results_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin()
```
The "bwt" model has the lowest RMSE distribution overall, indicating including as much as related variables likely performs better than the other models in terms of prediction accuracy. The "interaction" model has a slightly higher RMSE compared with "bwt" model, indicating the performance of prediction accuracy could be be improved. The "main_effect" model has the highest RMSE and the widest spread, indicating poor performance of prediction accuracy and we might need more variables to improve the prediction accuracy. 
